Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-02-29 demystify.tex
updates

\begin{domesticbox}[Domestic students:] If you're a domestic student, you have several advantages in your application.  First, we already know about your school (see \autoref{sec:your-school}), and you are also more familiar with the US education system and culture.  You also have more opportunities for funding, e.g., through government scholarships for US citizens and residents. Finally, compared to international students, PhD applications in CS from domestic students are few and that can really help your case.
\end{domesticbox}

@@

>>>>

@@

Most of what is written in this document is applicable to both domestic\footnote{Domestic simply means you did your undergrad (or MS) at a US university.} and international students.  However, there are some differences that domestic students should be aware of.  This section lists some of these differences.

\section{Application Materials}

\paragraph{Fee Waiving} Some school might offer application fee waiver for domestic students.  You should check with the school you're applying to.

\paragraph{School \autoref{sec:your-school}} we already know about your school, which is a plus (see \autoref{sec:your-school}). You are also more familiar with the US education system and culture (so hopefully you are aware of the cultural issues listed in \autoref{sec:cultural}).

\paragraph{Standard Tests \autoref{sec:grades}} You do not need to take TOEFL or IELTS because you already did your undergrad (or MS).

\paragraph{Transcripts} You do not need to get your transcripts evaluated by WES or other services (which can be a hassle and inaccurate).  You can just send your official transcripts directly to the school you're applying to.

\paragraph{Funding \S\ref{sec:funding}} You have more opportunities for funding, e.g., through government scholarships for US citizens and residents.  You can also apply to specific programs \emph{before} you start your PhD, e.g., NSF Graduate Research Fellowship Program (GRFP) and Hertz Foundation Fellowship.  These fellowships can be very competitive and will improve your admission chance if you get them.

\paragraph{Research Experiences} You might have more research experiences than international students. For example, you likely have many opportunities to do research as an undergraduates, e.g., through REUs and internships.  You should highlight these experiences in your application.

\paragraph{Standing out} There are very few domestic applications compared to international ones (i.e., domestic students are minority in the CS PhD application pool).  That makes you stand out and can really help your case.

% \begin{domesticbox}[Domestic students:] If you're a domestic student, you have several advantages in your application.   You also have more opportunities for funding, e.g., through government scholarships for US citizens and residents. Finally,
% \end{domesticbox}
